\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-16 bare_conf.tex
some changes according to reviews.

\textcolor{red}{We begin our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research. Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system. Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}
% corr end

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way. USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}. The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks. While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband. The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind. On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally. Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.

>>>>

\textcolor{red}{We begin our presentation with Section~\ref{sec:method}, describing the methodological foundations of this research. Section~\ref{sec:results} focuses on the architecture of the suggested human vision compensation system. Finally, Section~\ref{sec:discussion} summarizes and discusses the results of the conducted analysis.}

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{: for example, adsd .} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

Similar functionality has been previously addressed by research communities \cite{Caraiman}-\cite{Zientara} and industry \cite{orcam}\cite{horus}. The main difference between the aforementioned commercial solutions and the proposed system is the ability to utilize external resources for computationally intensive image or video processing tasks. While the availability of the computational power could be seen as the main advantage, it comes with high cost - dependency on a well-functioning mobile broadband. The development of the high-speed mobile networks (4G and 5G in the nearest future) is likely to make the major limitation of the proposed architecture obsolete, especially in densely populated areas containing many hazards for the blind. On the other side, increasing computational capacity of smartphones also may allow to conduct more advanced image or video processing locally. \textcolor{red}{Although not always technically possible for more complex algorithm systems, local  implementations are especially important in areas, where wireless Internet connectivity is not available, since they allow to preserve at least partial functionality of the system.} Combined audio/tactile interface may also be more convenient for the users, allowing to provide feedback in a more efficient way than using tactile or audio interfaces separately.
